ERSPAN Support for Linux

### 2018-10-18 paper.tex
minor fixes
wip: add openvswitch impl section

%\noindent
\textbf{Implementation: }
Type II introduces two new configurable fields to netlink API;
the Session ID and Index.
Session ID is configured by users through iproute2 tool with netlink API. 
Since ERSPAN does not use the GRE Key field, we re-use the
\texttt{IFLA\_GRE\_IKEY, IFLA\_GRE\_OKEY} as the session ID field.
Index is also configurable by users through iproute2.
The COS field and VLAN field are extrated from the original frame and set
properly.  The truncate bit is detected by comparing the the mirrored frame's
skb->len and the length its IP header reports~\cite{erspantruncate}.
%commit: erspan: auto detect truncated packets.

@@

\section{Example Use Case}
\begin{figure}
{\scriptsize
\begin{verbatim}
 session 10            Linux, session 20        Linux, session 30
+----------+         +-------------------+      +----------------+
| Physical |         |     VM1  VM2 ...  |      |     linux      |
| Machines |         | 10.1.1.3  |       |      |   netdev,eth1  |
+----------+         |  +--------------+ |      |      |         |
    | links          |  | Open vSwitch | |      | ERSPAN 10.1.1.4|
    | 10.1.1.2       |  +--------------+ |      | netdev         |
+------------+       +-------||----------+      +-||------------+ 
|Cisco switch|               ||                   ||
+------------+               || ERSPAN            || ERSPAN
   || ERSPAN tunnel          || tunnel            || tunnel
   || (192.168.1.2)          || (192.168.1.3)     || (192.168.1.4)
    /~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\     +-------+ 
    {       Layer 3 IPv4, Ipv6 network             } === |Traffic|
    \~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~/     |Sniffer|
                192.168.1.*                              +-------+
                                                        192.168.1.1
\end{verbatim}   
}
\vspace{-0.5em}
\caption{Example of creating three ERSPAN monitoring sessions, $10, 20, 30$,
in a $10.1.1.*$ internal network, mirroring traffic over a $192.168.1.*$ IP network.}
\label{example}
\vspace{-1.0em}
\end{figure}

>>>>

%\noindent
\textbf{Implementation: }
Type II introduces two new configurable fields to netlink API;
the Session ID and Index.
Session ID is configured by users through iproute2 tool with netlink API. 
Since ERSPAN does not use the GRE Key field, we re-use the
\texttt{IFLA\_GRE\_IKEY, IFLA\_GRE\_OKEY} as the session ID field.
Index is also configurable by users through iproute2.
The COS field and VLAN field are extrated from the original frame and set
properly.  The truncate bit is detected by comparing the the mirrored frame's
\texttt{skb->len} and the length its IP header reports.
%commit: erspan: auto detect truncated packets.

@@

\mycomment{
\subsection{Open vSwitch Kernel Module}
%configuration
Similar to other tunnel types such as VxLAN and Geneve,
Open vSwitch kernel module, openvswitch.ko, configures the Linux
ERSPAN tunnel by getting the binary tunnel configuration blob from
its userspace daemon, ovs-vswitchd, verifies its parameters, and
copies the tunnel data into flow key (struct sw\_flow\_key).
As a result, the tunnel configuration is per-flow key set-up.

When OVS kernel module process 
% struct ip_tunnel_info

% describe how OVS uses it
% /net/openvswitch/flow_netlink.c
commit fc1372f89ffe1f58b589643b75f679e452350703
Author: William Tu <u9012063@gmail.com>
Date:   Thu Jan 25 13:20:11 2018 -0800

    openvswitch: add erspan version I and II support

    The patch adds support for openvswitch to configure erspan
 %   v1 and v2.  The OVS_TUNNEL_KEY_ATTR_ERSPAN_OPTS attr is added
    to uapi as a binary blob to support all ERSPAN v1 and v2's
    fields.  Note that Previous commit "openvswitch: Add erspan tunnel
    support." was reverted since it does not design properly.

}
\section{Example Use Case}
\begin{figure}
{\scriptsize
\begin{verbatim}
 session 10            Linux, session 20        Linux, session 30
+----------+         +-------------------+      +----------------+
| Physical |         |     VM1  VM2 ...  |      |     linux      |
| Machines |         | 10.1.1.3  |       |      |   netdev,eth1  |
+----------+         |  +--------------+ |      |      |         |
    | links          |  | Open vSwitch | |      | ERSPAN 10.1.1.4|
    | 10.1.1.2       |  +--------------+ |      | netdev         |
+------------+       +-------||----------+      +-||------------+ 
|Cisco switch|               ||                   ||
+------------+               || ERSPAN            || ERSPAN
   || ERSPAN tunnel          || tunnel            || tunnel
   || (192.168.1.2)          || (192.168.1.3)     || (192.168.1.4)
    /~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\     +-------+ 
    {       Layer 3 IPv4, Ipv6 network             } === |Traffic|
    \~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~/     |Sniffer|
                192.168.1.*                              +-------+
                                                        192.168.1.1
\end{verbatim}   
}
\vspace{-0.5em}
\caption{Example of creating three ERSPAN monitoring sessions, $10, 20, 30$,
in a $10.1.1.*$ internal network, mirroring traffic over a $192.168.1.*$ IP network.}
\label{example}
\vspace{-1.0em}
\end{figure}
